Calculating life expectancy and exploring missingness

### 2016-11-04 Code/1_Explore_Data_v2.Rmd
added heatmaps to explore NA cods

```{r addvar_cod_proportions}
dat.clean <- dat.clean %>% group_by(State2, RaceSex, Year3, Age3) %>%
                           arrange(State2, RaceSex, Year3, Age3) %>%
                           mutate(total_deaths1 = sum(Count_md1),
                                  total_deaths5 = sum(Count_md5),
                                  total_deaths9 = sum(Count_md9),
                                  cod_prop_death1 = Count_md1/total_deaths1, 
                                  cod_prop_death5 = Count_md5/total_deaths5,
                                  cod_prop_death9 = Count_md9/total_deaths9)
```

To calculate life expectancy, we have to aggregate the data across the causes of death.

>>>>

```{r addvar_cod_proportions}
dat.clean <- dat.clean %>% group_by(State2, RaceSex, Year3, Age3) %>%
                           arrange(State2, RaceSex, Year3, Age3) %>%
                           mutate(total_deaths1 = sum(Count_md1),
                                  total_deaths5 = sum(Count_md5),
                                  total_deaths9 = sum(Count_md9),
                                  cod_prop_death1 = Count_md1/total_deaths1, 
                                  cod_prop_death5 = Count_md5/total_deaths5,
                                  cod_prop_death9 = Count_md9/total_deaths9)

length(dat.clean$total_deaths5[dat.clean$total_deaths5 == 0])
summary(dat.clean$cod_prop_death5[dat.clean$total_deaths5 == 0])
#76998 strata with 0 deaths from any cause (12833 when divided by 6 -- the number of causes)
#7% of strata have no deaths from any cause.
```

To calculate life expectancy, we have to aggregate the data across causes of death.
